---
title: "PDMPs for MMD Copula"
author: "Jack Jewson"
date: "7 May 2024"
output: html_document
---

## Preamble {.tabset}

### Working directory

+ Change this to be the directory that the stan files are saved in 

```{r setwd, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

my_dir <- "C:/Users/jjew0003/Documents/Monash_Yr1/PDMPs_IntractableLikelihood/"


```

### Packages

Loading the required packages.

```{r packages, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}
library(LaplacesDemon)

library(mvtnorm)
```


### RCPP

```{r RCPP, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}
library(Rcpp)

setwd(my_dir)

sourceCpp("MMD_copula_indirect_arma.cpp")
```

# Gaussian Data - n = 100 {.tabset}

## Data

```{r data_sim_MVGaussian_n100, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}
set.seed(1)

N_rep <- 1

theta <- 0.5 # we may get into trouble for theta not equal to 0.5
p <- 2

n <- 100

y <- rmvnorm(n, rep(0, 2), diag(1 - theta, p) + matrix(theta, nrow = p, ncol = p))

```

## PDMP 


### set-up 

```{r copula_setup_n100, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

u_hat <- matrix(NA, nrow = n, ncol = p)
for(j in 1:p){
  for(i in 1:n){
    u_hat[i,j] <- length(which(y[,j] <= y[i,j]))/n
  }
  
}

#gamma <- 1
gamma <- 0.25

plot(u_hat[,1], u_hat[,2])

R <- 3
```

## m = 5 (Rcpp)

```{r copula_skeleton_m5_n100, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}


m <- 5

#T_end <- 100
T_end <- 4000
xi_0 <- 0
theta_0 <- 1

a <- 1
b <- 1


timer_MMD_copula_m5_rcpp.start <- Sys.time()
skeleton_copula_IntractLik_m5_rcpp <- ZigZag_MMD_RBF_biGaussian_copula_cpp_arma(T_end, array(xi_0, dim = c(1)), array(theta_0, dim = c(1)), u_hat, m, gamma, R, w = 1, a, b, N_skeleton = 100000)
timer_MMD_copula_m5_rcpp.end <- Sys.time()

sample_copula_IntractLik_m5_rcpp <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_copula_IntractLik_m5_rcpp$skeleton_T, skeleton_Xi = skeleton_copula_IntractLik_m5_rcpp$skeleton_Xi, skeleton_Theta = skeleton_copula_IntractLik_m5_rcpp$skeleton_Theta, N = 5000)


```

```{r copula_skeleton_m5_n100_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}
difftime(timer_MMD_copula_m5_rcpp.end, timer_MMD_copula_m5_rcpp.start, units = "mins")

skeleton_copula_IntractLik_m5_rcpp$max_alpha
skeleton_copula_IntractLik_m5_rcpp$mean_alpha

plot(density(sample_copula_IntractLik_m5_rcpp[,1]), ylab = "Density", xlab = "xi", lwd = 3, main = paste("Copula"))

plot(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[,1])) - 1), ylab = "Density", xlab = "theta", lwd = 3, main = paste("Copula"))
abline(v = theta, lwd = 3, lty = 2, col = "red")


ESS(sample_copula_IntractLik_m5_rcpp[,1])

```

## m = 20 (Rcpp)

```{r copula_skeleton_m20_n100, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

m <- 20

#T_end <- 100
T_end <- 4000
xi_0 <- 0
theta_0 <- 1

a <- 1
b <- 1


timer_MMD_copula_m20_rcpp.start <- Sys.time()
skeleton_copula_IntractLik_m20_rcpp <- ZigZag_MMD_RBF_biGaussian_copula_cpp_arma(T_end, array(xi_0, dim = c(1)), array(theta_0, dim = c(1)), u_hat, m, gamma, R, w = 1, a, b, N_skeleton = 100000)
timer_MMD_copula_m20_rcpp.end <- Sys.time()

sample_copula_IntractLik_m20_rcpp <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_copula_IntractLik_m20_rcpp$skeleton_T, skeleton_Xi = skeleton_copula_IntractLik_m20_rcpp$skeleton_Xi, skeleton_Theta = skeleton_copula_IntractLik_m20_rcpp$skeleton_Theta, N = 5000)


```

```{r copula_skeleton_m20_n100_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}
difftime(timer_MMD_copula_m20_rcpp.end, timer_MMD_copula_m20_rcpp.start, units = "mins")

skeleton_copula_IntractLik_m20_rcpp$max_alpha
skeleton_copula_IntractLik_m20_rcpp$mean_alpha

plot(density(sample_copula_IntractLik_m5_rcpp[,1]), ylab = "Density", xlab = "xi", lwd = 3, main = paste("Copula"))
lines(density(sample_copula_IntractLik_m20_rcpp[,1]), lty = 2, lwd = 3)

plot(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[,1])) - 1), ylab = "Density", xlab = "theta", lwd = 3, main = paste("Copula"))
lines(density(2/(1+exp(-sample_copula_IntractLik_m20_rcpp[,1])) - 1), lty = 2, lwd = 3)
abline(v = theta, lwd = 3, lty = 2, col = "red")


ESS(sample_copula_IntractLik_m5_rcpp[,1])
ESS(sample_copula_IntractLik_m20_rcpp[,1])

```

## m = 50 (Rcpp)

```{r copula_skeleton_m50_n100, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

m <- 50

#T_end <- 100
T_end <- 4000
xi_0 <- 0
theta_0 <- 1

a <- 1
b <- 1


timer_MMD_copula_m50_rcpp.start <- Sys.time()
skeleton_copula_IntractLik_m50_rcpp <- ZigZag_MMD_RBF_biGaussian_copula_cpp_arma(T_end, array(xi_0, dim = c(1)), array(theta_0, dim = c(1)), u_hat, m, gamma, R, w = 1, a, b, N_skeleton = 100000)
timer_MMD_copula_m50_rcpp.end <- Sys.time()

sample_copula_IntractLik_m50_rcpp <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_copula_IntractLik_m50_rcpp$skeleton_T, skeleton_Xi = skeleton_copula_IntractLik_m50_rcpp$skeleton_Xi, skeleton_Theta = skeleton_copula_IntractLik_m50_rcpp$skeleton_Theta, N = 5000)


```

```{r copula_skeleton_m50_n100_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}
difftime(timer_MMD_copula_m50_rcpp.end, timer_MMD_copula_m50_rcpp.start, units = "mins")

skeleton_copula_IntractLik_m50_rcpp$max_alpha
skeleton_copula_IntractLik_m50_rcpp$mean_alpha

plot(density(sample_copula_IntractLik_m5_rcpp[,1]), ylab = "Density", xlab = "xi", lwd = 3, main = paste("Copula"))
lines(density(sample_copula_IntractLik_m20_rcpp[,1]), lty = 2, lwd = 3)
lines(density(sample_copula_IntractLik_m50_rcpp[,1]), lty = 3, lwd = 3)

plot(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[,1])) - 1), ylab = "Density", xlab = "theta", lwd = 3, main = paste("Copula"))
lines(density(2/(1+exp(-sample_copula_IntractLik_m20_rcpp[,1])) - 1), lty = 2, lwd = 3)
lines(density(2/(1+exp(-sample_copula_IntractLik_m50_rcpp[,1])) - 1), lty = 3, lwd = 3)
abline(v = theta, lwd = 3, lty = 2, col = "red")


ESS(sample_copula_IntractLik_m5_rcpp[,1])
ESS(sample_copula_IntractLik_m20_rcpp[,1])
ESS(sample_copula_IntractLik_m50_rcpp[,1])

```


```{r copula_skeleton_m50_n100_diag_tikz, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 3, fig.width = 5, dev = "tikz"}
par(mar = c(3.5, 3.8, 1.5, 1.1)) # bottom, left, top, right
par(mgp = c(2.15, 1, 0))
par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)

plot(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[,1])) - 1), ylab = "Density", xlab = "$\\theta$", lwd = 3, main = paste("Copula $n =$", n), ylim = c(0, 1.25))
lines(density(2/(1+exp(-sample_copula_IntractLik_m20_rcpp[,1])) - 1), lty = 2, lwd = 3, col = "darkgray")
lines(density(2/(1+exp(-sample_copula_IntractLik_m50_rcpp[,1])) - 1), lty = 3, lwd = 3, col = "lightgray")
abline(v = theta, lwd = 3, lty = 2, col = "red")
legend("topleft", c("$m = 5$", "$m = 20$", "$m = 50$"), lty = c(1, 2, 3), col = c("black", "darkgray", "lightgray"), bty = "n")


```

# Gaussian Data - n = 100 - Repeated MCMC {.tabset}

## Data

```{r data_sim_MVGaussian_n100_rep, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}
set.seed(1)

N_rep <- 1

theta <- 0.5 # we may get into trouble for theta not equal to 0.5
p <- 2

n <- 100

y <- rmvnorm(n, rep(0, 2), diag(1 - theta, p) + matrix(theta, nrow = p, ncol = p))

```

## set-up 

```{r copula_setup_n100_rep, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

u_hat <- matrix(NA, nrow = n, ncol = p)
for(j in 1:p){
  for(i in 1:n){
    u_hat[i,j] <- length(which(y[,j] <= y[i,j]))/n
  }
  
}

#gamma <- 1
gamma <- 0.25


plot(u_hat[,1], u_hat[,2])

R <- 3

N_rep <- 25

```

## m = 5 (Rcpp)

```{r copula_skeleton_m5_n100_rep, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

m <- 5

#T_end <- 100
T_end <- 4000

a <- 1
b <- 1

set.seed(1)

sample_copula_IntractLik_m5_rcpp <- list()
timer_copula_IntractLik_m5_rcpp <- rep(NA, N_rep)
max_alpha_copula_IntractLik_m5_rcpp <- rep(NA, N_rep)
mean_alpha_copula_IntractLik_m5_rcpp <- rep(NA, N_rep)
ESS_copula_IntractLik_m5_rcpp <- rep(NA, N_rep)

for(j in 1:N_rep){

  xi_0 <- rnorm(1, 0, 1)
  theta_0 <- sample(c(-1, 1), 1)

  timer_MMD_copula_m5_rcpp.start <- Sys.time()
  skeleton_copula_IntractLik_m5_rcpp <- ZigZag_MMD_RBF_biGaussian_copula_cpp_arma(T_end, array(xi_0, dim = c(1)), array(theta_0, dim = c(1)), u_hat, m, gamma, R, w = 1, a, b, N_skeleton = 100000)
  timer_MMD_copula_m5_rcpp.end <- Sys.time()
  
  timer_copula_IntractLik_m5_rcpp[j] <- difftime(timer_MMD_copula_m5_rcpp.end, timer_MMD_copula_m5_rcpp.start, units = "mins")
  
  max_alpha_copula_IntractLik_m5_rcpp[j] <- skeleton_copula_IntractLik_m5_rcpp$max_alpha
  mean_alpha_copula_IntractLik_m5_rcpp[j] <- skeleton_copula_IntractLik_m5_rcpp$mean_alpha

  sample_copula_IntractLik_m5_rcpp[[j]] <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_copula_IntractLik_m5_rcpp$skeleton_T, skeleton_Xi = skeleton_copula_IntractLik_m5_rcpp$skeleton_Xi, skeleton_Theta = skeleton_copula_IntractLik_m5_rcpp$skeleton_Theta, N = 5000)
  
  ESS_copula_IntractLik_m5_rcpp[j] <- ESS(sample_copula_IntractLik_m5_rcpp[[j]][,1])
  
  cat("Repeat", j, "done", "\n")
}



```

```{r copula_skeleton_m5_n100_rep_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

mean(timer_copula_IntractLik_m5_rcpp)
mean(ESS_copula_IntractLik_m5_rcpp)

mean(mean_alpha_copula_IntractLik_m5_rcpp)
max(max_alpha_copula_IntractLik_m5_rcpp)


plot(density(sample_copula_IntractLik_m5_rcpp[[1]][,1]), ylab = "Density", xlab = "xi", lwd = 3, main = paste("Copula n =", n, "m =", m))
for(j in 2:N_rep){
  lines(density(sample_copula_IntractLik_m5_rcpp[[j]][,1]), lwd = 3)
}

plot(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[[1]][,1])) - 1), ylab = "Density", xlab = "theta", lwd = 3, main = paste("Copula n =", n, "m =", m))
for(j in 2:N_rep){
  lines(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[[j]][,1])) - 1), lwd = 3)
}
abline(v = theta, lwd = 3, lty = 2, col = "red")




```

```{r copula_skeleton_m5_n100_rep_diag_tikz, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 3, fig.width = 5, dev = "tikz"}
par(mar = c(3.5, 3.8, 1.5, 1.1)) # bottom, left, top, right
par(mgp = c(2.15, 1, 0))
par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)

plot(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[[1]][,1])) - 1), ylab = "Density", xlab = "$\\theta$", lwd = 3, main = paste("Copula $n =$", n, "$m =$", m), ylim = c(0, 1.25), xlim = c(-1, 1))
for(j in 2:N_rep){
  lines(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[[j]][,1])) - 1), lwd = 3)
}
abline(v = theta, lwd = 3, lty = 2, col = "red")


```

## m = 20 (Rcpp)

```{r copula_skeleton_m20_n100_rep, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

m <- 20

#T_end <- 100
T_end <- 4000

a <- 1
b <- 1

set.seed(1)

sample_copula_IntractLik_m20_rcpp <- list()
timer_copula_IntractLik_m20_rcpp <- rep(NA, N_rep)
max_alpha_copula_IntractLik_m20_rcpp <- rep(NA, N_rep)
mean_alpha_copula_IntractLik_m20_rcpp <- rep(NA, N_rep)
ESS_copula_IntractLik_m20_rcpp <- rep(NA, N_rep)

for(j in 1:N_rep){

  xi_0 <- rnorm(1, 0, 1)
  theta_0 <- sample(c(-1, 1), 1)

  timer_MMD_copula_m20_rcpp.start <- Sys.time()
  skeleton_copula_IntractLik_m20_rcpp <- ZigZag_MMD_RBF_biGaussian_copula_cpp_arma(T_end, array(xi_0, dim = c(1)), array(theta_0, dim = c(1)), u_hat, m, gamma, R, w = 1, a, b, N_skeleton = 100000)
  timer_MMD_copula_m20_rcpp.end <- Sys.time()
  
  timer_copula_IntractLik_m20_rcpp[j] <- difftime(timer_MMD_copula_m20_rcpp.end, timer_MMD_copula_m20_rcpp.start, units = "mins")
  
  max_alpha_copula_IntractLik_m20_rcpp[j] <- skeleton_copula_IntractLik_m20_rcpp$max_alpha
  mean_alpha_copula_IntractLik_m20_rcpp[j] <- skeleton_copula_IntractLik_m20_rcpp$mean_alpha

  sample_copula_IntractLik_m20_rcpp[[j]] <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_copula_IntractLik_m20_rcpp$skeleton_T, skeleton_Xi = skeleton_copula_IntractLik_m20_rcpp$skeleton_Xi, skeleton_Theta = skeleton_copula_IntractLik_m20_rcpp$skeleton_Theta, N = 5000)
  
  ESS_copula_IntractLik_m20_rcpp[j] <- ESS(sample_copula_IntractLik_m20_rcpp[[j]][,1])
  
  cat("Repeat", j, "done", "\n")
}



```

```{r copula_skeleton_m20_n100_rep_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

mean(timer_copula_IntractLik_m20_rcpp)
mean(ESS_copula_IntractLik_m20_rcpp)

mean(mean_alpha_copula_IntractLik_m20_rcpp)
max(max_alpha_copula_IntractLik_m20_rcpp)


plot(density(sample_copula_IntractLik_m20_rcpp[[1]][,1]), ylab = "Density", xlab = "xi", lwd = 3, main = paste("Copula n =", n, "m =", m))
for(j in 2:N_rep){
  lines(density(sample_copula_IntractLik_m20_rcpp[[j]][,1]), lwd = 3)
}

plot(density(2/(1+exp(-sample_copula_IntractLik_m20_rcpp[[1]][,1])) - 1), ylab = "Density", xlab = "theta", lwd = 3, main = paste("Copula n =", n, "m =", m))
for(j in 2:N_rep){
  lines(density(2/(1+exp(-sample_copula_IntractLik_m20_rcpp[[j]][,1])) - 1), lwd = 3)
}
abline(v = theta, lwd = 3, lty = 2, col = "red")




```

```{r copula_skeleton_m20_n100_rep_diag_tikz, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 3, fig.width = 5, dev = "tikz"}
par(mar = c(3.5, 3.8, 1.5, 1.1)) # bottom, left, top, right
par(mgp = c(2.15, 1, 0))
par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)

plot(density(2/(1+exp(-sample_copula_IntractLik_m20_rcpp[[1]][,1])) - 1), ylab = "Density", xlab = "$\\theta$", lwd = 3, main = paste("Copula $n =$", n, "$m =$", m), ylim = c(0, 1.25), xlim = c(-1, 1))
for(j in 2:N_rep){
  lines(density(2/(1+exp(-sample_copula_IntractLik_m20_rcpp[[j]][,1])) - 1), lwd = 3)
}
abline(v = theta, lwd = 3, lty = 2, col = "red")


```

# Gaussian Data - n = 500 {.tabset}

## Data

```{r data_sim_MVGaussian_n500, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}
set.seed(1)

N_rep <- 1

theta <- 0.5 # we may get into trouble for theta not equal to 0.5
p <- 2

n <- 500

y <- rmvnorm(n, rep(0, 2), diag(1 - theta, p) + matrix(theta, nrow = p, ncol = p))

```


## PDMP 

### set-up 

```{r copula_setup_n500, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

u_hat <- matrix(NA, nrow = n, ncol = p)
for(j in 1:p){
  for(i in 1:n){
    u_hat[i,j] <- length(which(y[,j] <= y[i,j]))/n
  }
  
}

#gamma <- 1
gamma <- 0.25


plot(u_hat[,1], u_hat[,2])

R <- 3



```

## m = 5 (Rcpp)

```{r copula_skeleton_m5_n500, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

m <- 5

#T_end <- 100
T_end <- 2000
xi_0 <- 0
theta_0 <- 1

a <- 1
b <- 1


timer_MMD_copula_m5_rcpp.start <- Sys.time()
skeleton_copula_IntractLik_m5_rcpp <- ZigZag_MMD_RBF_biGaussian_copula_cpp_arma(T_end, array(xi_0, dim = c(1)), array(theta_0, dim = c(1)), u_hat, m, gamma, R, w = 1, a, b, N_skeleton = 100000)
timer_MMD_copula_m5_rcpp.end <- Sys.time()

sample_copula_IntractLik_m5_rcpp <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_copula_IntractLik_m5_rcpp$skeleton_T, skeleton_Xi = skeleton_copula_IntractLik_m5_rcpp$skeleton_Xi, skeleton_Theta = skeleton_copula_IntractLik_m5_rcpp$skeleton_Theta, N = 5000)

```

```{r copula_skeleton_m5_n500_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}
difftime(timer_MMD_copula_m5_rcpp.end, timer_MMD_copula_m5_rcpp.start, units = "mins")

skeleton_copula_IntractLik_m5_rcpp$max_alpha
skeleton_copula_IntractLik_m5_rcpp$mean_alpha

plot(density(sample_copula_IntractLik_m5_rcpp[,1]), ylab = "Density", xlab = "xi", lwd = 3, main = paste("Copula"))

plot(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[,1])) - 1), ylab = "Density", xlab = "theta", lwd = 3, main = paste("Copula"))
abline(v = theta, lwd = 3, lty = 2, col = "red")


ESS(sample_copula_IntractLik_m5_rcpp[,1])

```

## m = 20 (Rcpp)

```{r copula_skeleton_m20_n500, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

m <- 20

#T_end <- 100
T_end <- 2000
xi_0 <- 0
theta_0 <- 1

a <- 1
b <- 1


timer_MMD_copula_m20_rcpp.start <- Sys.time()
skeleton_copula_IntractLik_m20_rcpp <- ZigZag_MMD_RBF_biGaussian_copula_cpp_arma(T_end, array(xi_0, dim = c(1)), array(theta_0, dim = c(1)), u_hat, m, gamma, R, w = 1, a, b, N_skeleton = 100000)
timer_MMD_copula_m20_rcpp.end <- Sys.time()

sample_copula_IntractLik_m20_rcpp <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_copula_IntractLik_m20_rcpp$skeleton_T, skeleton_Xi = skeleton_copula_IntractLik_m20_rcpp$skeleton_Xi, skeleton_Theta = skeleton_copula_IntractLik_m20_rcpp$skeleton_Theta, N = 5000)

```

```{r copula_skeleton_m20_n500_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}
difftime(timer_MMD_copula_m20_rcpp.end, timer_MMD_copula_m20_rcpp.start, units = "mins")

skeleton_copula_IntractLik_m20_rcpp$max_alpha
skeleton_copula_IntractLik_m20_rcpp$mean_alpha

plot(density(sample_copula_IntractLik_m5_rcpp[,1]), ylab = "Density", xlab = "xi", lwd = 3, main = paste("Copula"))
lines(density(sample_copula_IntractLik_m20_rcpp[,1]), lty = 2, lwd = 3)

plot(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[,1])) - 1), ylab = "Density", xlab = "theta", lwd = 3, main = paste("Copula"))
lines(density(2/(1+exp(-sample_copula_IntractLik_m20_rcpp[,1])) - 1), lty = 2, lwd = 3)
abline(v = theta, lwd = 3, lty = 2, col = "red")


ESS(sample_copula_IntractLik_m5_rcpp[,1])
ESS(sample_copula_IntractLik_m20_rcpp[,1])

```

## m = 50 (Rcpp)

```{r copula_skeleton_m50_n500, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

m <- 50

#T_end <- 100
T_end <- 2000
xi_0 <- 0
theta_0 <- 1

a <- 1
b <- 1


timer_MMD_copula_m50_rcpp.start <- Sys.time()
skeleton_copula_IntractLik_m50_rcpp <- ZigZag_MMD_RBF_biGaussian_copula_cpp_arma(T_end, array(xi_0, dim = c(1)), array(theta_0, dim = c(1)), u_hat, m, gamma, R, w = 1, a, b, N_skeleton = 100000)
timer_MMD_copula_m50_rcpp.end <- Sys.time()

sample_copula_IntractLik_m50_rcpp <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_copula_IntractLik_m50_rcpp$skeleton_T, skeleton_Xi = skeleton_copula_IntractLik_m50_rcpp$skeleton_Xi, skeleton_Theta = skeleton_copula_IntractLik_m50_rcpp$skeleton_Theta, N = 5000)

```

```{r copula_skeleton_m50_n500_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}
difftime(timer_MMD_copula_m50_rcpp.end, timer_MMD_copula_m50_rcpp.start, units = "mins")

skeleton_copula_IntractLik_m50_rcpp$max_alpha
skeleton_copula_IntractLik_m50_rcpp$mean_alpha

plot(density(sample_copula_IntractLik_m5_rcpp[,1]), ylab = "Density", xlab = "xi", lwd = 3, main = paste("Copula"))
lines(density(sample_copula_IntractLik_m20_rcpp[,1]), lty = 2, lwd = 3)
lines(density(sample_copula_IntractLik_m50_rcpp[,1]), lty = 3, lwd = 3)

plot(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[,1])) - 1), ylab = "Density", xlab = "theta", lwd = 3, main = paste("Copula"))
lines(density(2/(1+exp(-sample_copula_IntractLik_m20_rcpp[,1])) - 1), lty = 2, lwd = 3)
lines(density(2/(1+exp(-sample_copula_IntractLik_m50_rcpp[,1])) - 1), lty = 3, lwd = 3)
abline(v = theta, lwd = 3, lty = 2, col = "red")


ESS(sample_copula_IntractLik_m5_rcpp[,1])
ESS(sample_copula_IntractLik_m20_rcpp[,1])
ESS(sample_copula_IntractLik_m50_rcpp[,1])

```

```{r copula_skeleton_m50_n500_diag_tikz, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 3, fig.width = 5, dev = "tikz"}
par(mar = c(3.5, 3.8, 1.5, 1.1)) # bottom, left, top, right
par(mgp = c(2.15, 1, 0))
par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)

plot(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[,1])) - 1), ylab = "Density", xlab = "$\\theta$", lwd = 3, main = paste("Copula $n =$", n), ylim = c(0, 2.5))
lines(density(2/(1+exp(-sample_copula_IntractLik_m20_rcpp[,1])) - 1), lty = 2, lwd = 3, col = "darkgray")
lines(density(2/(1+exp(-sample_copula_IntractLik_m50_rcpp[,1])) - 1), lty = 3, lwd = 3, col = "lightgray")
abline(v = theta, lwd = 3, lty = 2, col = "red")
#legend("topleft", c("$m = 5$", "$m = 20$", "$m = 50$"), lty = c(1, 2, 3), col = c("black", "darkgray", "lightgray"), bty = "n")


```


# Gaussian Data - n = 500 - Repeated MCMC {.tabset}

## Data

```{r data_sim_MVGaussian_n500_rep, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}
set.seed(1)

N_rep <- 1

theta <- 0.5 # we may get into trouble for theta not equal to 0.5
p <- 2

n <- 500

y <- rmvnorm(n, rep(0, 2), diag(1 - theta, p) + matrix(theta, nrow = p, ncol = p))

```

## set-up 

```{r copula_setup_n500_rep, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

u_hat <- matrix(NA, nrow = n, ncol = p)
for(j in 1:p){
  for(i in 1:n){
    u_hat[i,j] <- length(which(y[,j] <= y[i,j]))/n
  }
  
}

#gamma <- 1
gamma <- 0.25


plot(u_hat[,1], u_hat[,2])

R <- 3


N_rep <- 25


```

## m = 5 (Rcpp)

```{r copula_skeleton_m5_n500_rep, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

m <- 5

#T_end <- 100
T_end <- 2000

a <- 1
b <- 1

set.seed(1)

sample_copula_IntractLik_m5_rcpp <- list()
timer_copula_IntractLik_m5_rcpp <- rep(NA, N_rep)
max_alpha_copula_IntractLik_m5_rcpp <- rep(NA, N_rep)
mean_alpha_copula_IntractLik_m5_rcpp <- rep(NA, N_rep)
ESS_copula_IntractLik_m5_rcpp <- rep(NA, N_rep)

for(j in 1:N_rep){

  xi_0 <- rnorm(1, 0, 1)
  theta_0 <- sample(c(-1, 1), 1)

  timer_MMD_copula_m5_rcpp.start <- Sys.time()
  skeleton_copula_IntractLik_m5_rcpp <- ZigZag_MMD_RBF_biGaussian_copula_cpp_arma(T_end, array(xi_0, dim = c(1)), array(theta_0, dim = c(1)), u_hat, m, gamma, R, w = 1, a, b, N_skeleton = 100000)
  timer_MMD_copula_m5_rcpp.end <- Sys.time()
  
  timer_copula_IntractLik_m5_rcpp[j] <- difftime(timer_MMD_copula_m5_rcpp.end, timer_MMD_copula_m5_rcpp.start, units = "mins")
  
  max_alpha_copula_IntractLik_m5_rcpp[j] <- skeleton_copula_IntractLik_m5_rcpp$max_alpha
  mean_alpha_copula_IntractLik_m5_rcpp[j] <- skeleton_copula_IntractLik_m5_rcpp$mean_alpha

  sample_copula_IntractLik_m5_rcpp[[j]] <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_copula_IntractLik_m5_rcpp$skeleton_T, skeleton_Xi = skeleton_copula_IntractLik_m5_rcpp$skeleton_Xi, skeleton_Theta = skeleton_copula_IntractLik_m5_rcpp$skeleton_Theta, N = 5000)
  
  ESS_copula_IntractLik_m5_rcpp[j] <- ESS(sample_copula_IntractLik_m5_rcpp[[j]][,1])
  
  cat("Repeat", j, "done", "\n")
}

```

```{r copula_skeleton_m5_n500_rep_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

R

mean(timer_copula_IntractLik_m5_rcpp)
mean(ESS_copula_IntractLik_m5_rcpp)

mean(mean_alpha_copula_IntractLik_m5_rcpp)
max(max_alpha_copula_IntractLik_m5_rcpp)


plot(density(sample_copula_IntractLik_m5_rcpp[[1]][,1]), ylab = "Density", xlab = "xi", lwd = 3, main = paste("Copula n =", n, "m =", m))
for(j in 2:N_rep){
  lines(density(sample_copula_IntractLik_m5_rcpp[[j]][,1]), lwd = 3)
}

plot(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[[1]][,1])) - 1), ylab = "Density", xlab = "theta", lwd = 3, main = paste("Copula n =", n, "m =", m))
for(j in 2:N_rep){
  lines(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[[j]][,1])) - 1), lwd = 3)
}
abline(v = theta, lwd = 3, lty = 2, col = "red")




```

```{r copula_skeleton_m5_n500_rep_diag_tikz, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 3, fig.width = 5, dev = "tikz"}
par(mar = c(3.5, 3.8, 1.5, 1.1)) # bottom, left, top, right
par(mgp = c(2.15, 1, 0))
par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)

plot(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[[1]][,1])) - 1), ylab = "Density", xlab = "$\\theta$", lwd = 3, main = paste("Copula $n =$", n, "$m =$", m), ylim = c(0, 2.5), xlim = c(-0.2, 1))
for(j in 2:N_rep){
  lines(density(2/(1+exp(-sample_copula_IntractLik_m5_rcpp[[j]][,1])) - 1), lwd = 3)
}
abline(v = theta, lwd = 3, lty = 2, col = "red")


```

## m = 20 (Rcpp)

```{r copula_skeleton_m20_n500_rep, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

m <- 20

#T_end <- 100
T_end <- 2000

a <- 1
b <- 1

set.seed(1)

sample_copula_IntractLik_m20_rcpp <- list()
timer_copula_IntractLik_m20_rcpp <- rep(NA, N_rep)
max_alpha_copula_IntractLik_m20_rcpp <- rep(NA, N_rep)
mean_alpha_copula_IntractLik_m20_rcpp <- rep(NA, N_rep)
ESS_copula_IntractLik_m20_rcpp <- rep(NA, N_rep)

for(j in 1:N_rep){

  xi_0 <- rnorm(1, 0, 1)
  theta_0 <- sample(c(-1, 1), 1)

  timer_MMD_copula_m20_rcpp.start <- Sys.time()
  skeleton_copula_IntractLik_m20_rcpp <- ZigZag_MMD_RBF_biGaussian_copula_cpp_arma(T_end, array(xi_0, dim = c(1)), array(theta_0, dim = c(1)), u_hat, m, gamma, R, w = 1, a, b, N_skeleton = 100000)
  timer_MMD_copula_m20_rcpp.end <- Sys.time()
  
  timer_copula_IntractLik_m20_rcpp[j] <- difftime(timer_MMD_copula_m20_rcpp.end, timer_MMD_copula_m20_rcpp.start, units = "mins")
  
  max_alpha_copula_IntractLik_m20_rcpp[j] <- skeleton_copula_IntractLik_m20_rcpp$max_alpha
  mean_alpha_copula_IntractLik_m20_rcpp[j] <- skeleton_copula_IntractLik_m20_rcpp$mean_alpha

  sample_copula_IntractLik_m20_rcpp[[j]] <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_copula_IntractLik_m20_rcpp$skeleton_T, skeleton_Xi = skeleton_copula_IntractLik_m20_rcpp$skeleton_Xi, skeleton_Theta = skeleton_copula_IntractLik_m20_rcpp$skeleton_Theta, N = 5000)
  
  ESS_copula_IntractLik_m20_rcpp[j] <- ESS(sample_copula_IntractLik_m20_rcpp[[j]][,1])
  
  cat("Repeat", j, "done", "\n")
}

```

```{r copula_skeleton_m20_n500_rep_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

R

mean(timer_copula_IntractLik_m20_rcpp)
mean(ESS_copula_IntractLik_m20_rcpp)

mean(mean_alpha_copula_IntractLik_m20_rcpp)
max(max_alpha_copula_IntractLik_m20_rcpp)


plot(density(sample_copula_IntractLik_m20_rcpp[[1]][,1]), ylab = "Density", xlab = "xi", lwd = 3, main = paste("Copula n =", n, "m =", m))
for(j in 2:N_rep){
  lines(density(sample_copula_IntractLik_m20_rcpp[[j]][,1]), lwd = 3)
}

plot(density(2/(1+exp(-sample_copula_IntractLik_m20_rcpp[[1]][,1])) - 1), ylab = "Density", xlab = "theta", lwd = 3, main = paste("Copula n =", n, "m =", m))
for(j in 2:N_rep){
  lines(density(2/(1+exp(-sample_copula_IntractLik_m20_rcpp[[j]][,1])) - 1), lwd = 3)
}
abline(v = theta, lwd = 3, lty = 2, col = "red")




```

```{r copula_skeleton_m20_n500_rep_diag_tikz, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 3, fig.width = 5, dev = "tikz"}
par(mar = c(3.5, 3.8, 1.5, 1.1)) # bottom, left, top, right
par(mgp = c(2.15, 1, 0))
par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)

plot(density(2/(1+exp(-sample_copula_IntractLik_m20_rcpp[[1]][,1])) - 1), ylab = "Density", xlab = "$\\theta$", lwd = 3, main = paste("Copula $n =$", n, "$m =$", m), ylim = c(0, 2.5), xlim = c(-0.2, 1))
for(j in 2:N_rep){
  lines(density(2/(1+exp(-sample_copula_IntractLik_m20_rcpp[[j]][,1])) - 1), lwd = 3)
}
abline(v = theta, lwd = 3, lty = 2, col = "red")


```

