---
title: "PDMPs for MMD SBI with g-and-k distribution"
author: "Jack Jewson"
date: "19 Feb 2026"
output: html_document
---

## Preamble {.tabset}

### Working directory

+ Change this to be the directory that the stan files are saved in 

```{r setwd, include=TRUE,echo=TRUE, eval=TRUE,cache=TRUE}

my_dir <- "C:/Users/jjew0003/Documents/Monash_Yr1/PDMPs_IntractableLikelihood/"


```

### Packages

Loading the required packages.

```{r packages, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}
library(actuar)
library(metRology)
library(LaplacesDemon)

setwd(my_dir)

source("gandk/gandk.R")

source("gandk/median_heuristic.R")

library(dplyr)
library(ggplot2)
```


### RCPP

```{r RCPP, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}
library(Rcpp)

setwd(my_dir)

sourceCpp("gandk/MMD_arma_gandkV2.cpp")
```

### Transformations and the prior

I am worried that big distances are requires in $\xi$ in order to get a meaningful change in $\theta$

```{r}

xi_seq <- seq(-10, 10, length.out = 1000)

plot(xi_seq, exp(xi_seq)/((1+exp(xi_seq))^2), type = "l", xlab = "Xi", ylab = "Density")


plot(xi_seq, 5.0 / (1.0 + exp(-xi_seq)), xlab = "xi", ylab = "theta", type = "l")


```


# n = 100 {.tabset}

## Data generation

```{r data_sim_gandk_n100, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}
set.seed(123)
n <- 100
true_a <- 1.0
true_b <- 1.0
true_g <- 1.0
true_k <- 0.5

# Generate data using the R function
sim_data <- simulate_gandk_with_gradient(n, c(true_a, true_b, true_g, true_k))
y <- sim_data$samples
```

## PDMP 

### set-up 

```{r gandk_setup_n100, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

# Sampler parameters
gamma <- median_heuristic(cbind(y,y))
m <- 5 # Number of synthetic samples
T_end <- 5000
#T_end <- 100
w <- sqrt(2*pi)

# Helper function to transform from [0,5] to unconstrained
transform_to_unconstrained <- function(theta) {
  # θ = 5/(1+exp(-ξ)) => ξ = log(θ/(5-θ))
  log(theta / (5 - theta))
}

# Initial values on unconstrained scale
# Start near the middle of [0,5], e.g., at 2.5 for each parameter
xi_0 <- c(
  transform_to_unconstrained(1),  # a
  transform_to_unconstrained(1),  # b
  transform_to_unconstrained(1.0),  # g
  transform_to_unconstrained(1.0)   # k
)

theta_0 <- c(1, 1, 1, 1)  # Initial velocities

```

## m = 5 (Rcpp)

```{r gandk_skeleton_m5_n100, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

m <- 5


timer_MMD_gandk_m5.start <- Sys.time()
skeleton_gandk_IntractLik_m5 <- ZigZag_MMD_RBF_gandk_cpp_arma(T_end, xi_0, theta_0, y, m, gamma, w = w, N_skeleton = 100000)
timer_MMD_gandk_m5.end <- Sys.time()

sample_gandk_IntractLik_m5 <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_gandk_IntractLik_m5$skeleton_T, skeleton_Xi = skeleton_gandk_IntractLik_m5$skeleton_Xi, skeleton_Theta = skeleton_gandk_IntractLik_m5$skeleton_Theta, N = 1000)


sample_gandk_IntractLik_m5_theta <- transform_samples_to_original_scale(sample_gandk_IntractLik_m5)


```

```{r gandk_m5_n100_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}
difftime(timer_MMD_gandk_m5.end, timer_MMD_gandk_m5.start, units = "mins")

skeleton_gandk_IntractLik_m5$max_alpha
skeleton_gandk_IntractLik_m5$mean_alpha

## Unconstrained trace plots

plot(skeleton_gandk_IntractLik_m5$skeleton_T, skeleton_gandk_IntractLik_m5$skeleton_Xi[,1], type = "l", xlab = "T", ylab = "xi_a")

plot(skeleton_gandk_IntractLik_m5$skeleton_T, skeleton_gandk_IntractLik_m5$skeleton_Xi[,2], type = "l", xlab = "T", ylab = "xi_b")

plot(skeleton_gandk_IntractLik_m5$skeleton_T, skeleton_gandk_IntractLik_m5$skeleton_Xi[,3], type = "l", xlab = "T", ylab = "xi_g")

plot(skeleton_gandk_IntractLik_m5$skeleton_T, skeleton_gandk_IntractLik_m5$skeleton_Xi[,4], type = "l", xlab = "T", ylab = "xi_k")

## Constrained trace plots

plot(skeleton_gandk_IntractLik_m5$skeleton_T, transform_to_bounded_vec(skeleton_gandk_IntractLik_m5$skeleton_Xi[,1]), type = "l", xlab = "T", ylab = "a")

plot(skeleton_gandk_IntractLik_m5$skeleton_T, transform_to_bounded_vec(skeleton_gandk_IntractLik_m5$skeleton_Xi[,2]), type = "l", xlab = "T", ylab = "b")

plot(skeleton_gandk_IntractLik_m5$skeleton_T, transform_to_bounded_vec(skeleton_gandk_IntractLik_m5$skeleton_Xi[,3]), type = "l", xlab = "T", ylab = "g")

plot(skeleton_gandk_IntractLik_m5$skeleton_T, transform_to_bounded_vec(skeleton_gandk_IntractLik_m5$skeleton_Xi[,4]), type = "l", xlab = "T", ylab = "k")


## Density plots

plot(density(sample_gandk_IntractLik_m5_theta[,1]), ylab = "Density", xlab = paste0("a"), lwd = 3, main = paste("g-and-k"))
abline(v = true_a, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m5_theta[,2]), ylab = "Density", xlab = paste0("b"), lwd = 3, main = paste("g-and-k"))
abline(v = true_b, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m5_theta[,3]), ylab = "Density", xlab = paste0("g"), lwd = 3, main = paste("g-and-k"))
abline(v = true_g, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m5_theta[,4]), ylab = "Density", xlab = paste0("k"), lwd = 3, main = paste("g-and-k"))
abline(v = true_k, lwd = 3, lty = 2, col = "red")


ESS(sample_gandk_IntractLik_m5_theta[,1])
ESS(sample_gandk_IntractLik_m5_theta[,2])
ESS(sample_gandk_IntractLik_m5_theta[,3])
ESS(sample_gandk_IntractLik_m5_theta[,4])
```

## m = 20 (Rcpp)

```{r gandk_skeleton_m20_n100, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

m <- 20


timer_MMD_gandk_m20.start <- Sys.time()
skeleton_gandk_IntractLik_m20 <- ZigZag_MMD_RBF_gandk_cpp_arma(T_end, xi_0, theta_0, y, m, gamma, w = w, N_skeleton = 100000)
timer_MMD_gandk_m20.end <- Sys.time()

sample_gandk_IntractLik_m20 <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_gandk_IntractLik_m20$skeleton_T, skeleton_Xi = skeleton_gandk_IntractLik_m20$skeleton_Xi, skeleton_Theta = skeleton_gandk_IntractLik_m20$skeleton_Theta, N = 1000)


sample_gandk_IntractLik_m20_theta <- transform_samples_to_original_scale(sample_gandk_IntractLik_m20)


```

```{r gandk_m20_n100_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}
difftime(timer_MMD_gandk_m20.end, timer_MMD_gandk_m20.start, units = "mins")

skeleton_gandk_IntractLik_m20$max_alpha
skeleton_gandk_IntractLik_m20$mean_alpha

plot(density(sample_gandk_IntractLik_m20_theta[,1]), ylab = "Density", xlab = paste0("a"), lwd = 3, main = paste("g-and-k"))
abline(v = true_a, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m20_theta[,2]), ylab = "Density", xlab = paste0("b"), lwd = 3, main = paste("g-and-k"))
abline(v = true_b, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m20_theta[,3]), ylab = "Density", xlab = paste0("g"), lwd = 3, main = paste("g-and-k"))
abline(v = true_g, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m20_theta[,4]), ylab = "Density", xlab = paste0("k"), lwd = 3, main = paste("g-and-k"))
abline(v = true_k, lwd = 3, lty = 2, col = "red")


ESS(sample_gandk_IntractLik_m20_theta[,1])
ESS(sample_gandk_IntractLik_m20_theta[,2])
ESS(sample_gandk_IntractLik_m20_theta[,3])
ESS(sample_gandk_IntractLik_m20_theta[,4])
```

## m = 50  (Rcpp)

```{r gandk_skeleton_m50_n100, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

m <- 50


timer_MMD_gandk_m50.start <- Sys.time()
skeleton_gandk_IntractLik_m50 <- ZigZag_MMD_RBF_gandk_cpp_arma(T_end, xi_0, theta_0, y, m, gamma, w = w, N_skeleton = 100000)
timer_MMD_gandk_m50.end <- Sys.time()

sample_gandk_IntractLik_m50 <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_gandk_IntractLik_m50$skeleton_T, skeleton_Xi = skeleton_gandk_IntractLik_m50$skeleton_Xi, skeleton_Theta = skeleton_gandk_IntractLik_m50$skeleton_Theta, N = 1000)


sample_gandk_IntractLik_m50_theta <- transform_samples_to_original_scale(sample_gandk_IntractLik_m50)


```

```{r gandk_m50_n100_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

difftime(timer_MMD_gandk_m50.end, timer_MMD_gandk_m50.start, units = "mins")

skeleton_gandk_IntractLik_m50$max_alpha
skeleton_gandk_IntractLik_m50$mean_alpha

plot(density(sample_gandk_IntractLik_m50_theta[,1]), ylab = "Density", xlab = paste0("a"), lwd = 3, main = paste("g-and-k"))
abline(v = true_a, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m50_theta[,2]), ylab = "Density", xlab = paste0("b"), lwd = 3, main = paste("g-and-k"))
abline(v = true_b, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m50_theta[,3]), ylab = "Density", xlab = paste0("g"), lwd = 3, main = paste("g-and-k"))
abline(v = true_g, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m50_theta[,4]), ylab = "Density", xlab = paste0("k"), lwd = 3, main = paste("g-and-k"))
abline(v = true_k, lwd = 3, lty = 2, col = "red")


ESS(sample_gandk_IntractLik_m50_theta[,1])
ESS(sample_gandk_IntractLik_m50_theta[,2])
ESS(sample_gandk_IntractLik_m50_theta[,3])
ESS(sample_gandk_IntractLik_m50_theta[,4])
```

```{r gandk_n100_comparison, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

m5_df <- as.data.frame(sample_gandk_IntractLik_m5_theta) |> 
  mutate(m = rep(5, nrow(sample_gandk_IntractLik_m5_theta))) |>
  rename(a = V1, 
         b = V2, 
         g = V3, 
         k = V4)

m20_df <- as.data.frame(sample_gandk_IntractLik_m20_theta) |> 
  mutate(m = rep(20, nrow(sample_gandk_IntractLik_m20_theta))) |>
  rename(a = V1, 
         b = V2, 
         g = V3, 
         k = V4)

m50_df <- as.data.frame(sample_gandk_IntractLik_m50_theta) |> 
  mutate(m = rep(50, nrow(sample_gandk_IntractLik_m50_theta))) |>
  rename(a = V1, 
         b = V2, 
         g = V3, 
         k = V4)

m_comp_df <- bind_rows(m5_df, m20_df, m50_df)

m_comp_df |>
  mutate(m = as.factor(m)) |>
  ggplot(aes(x = a, color = m)) +
  geom_density(linewidth = 1.1) +
  geom_vline(xintercept = true_a) +
  ggtitle(paste0("g-and-k distribution n = ", n))

m_comp_df |>
  mutate(m = as.factor(m)) |>
  ggplot(aes(x = b, color = m)) +
  geom_density(linewidth = 1.1) +
  geom_vline(xintercept = true_b) +
  ggtitle(paste0("g-and-k distribution n = ", n))

m_comp_df |>
  mutate(m = as.factor(m)) |>
  ggplot(aes(x = g, color = m)) +
  geom_density(linewidth = 1.1) +
  geom_vline(xintercept = true_g) +
  ggtitle(paste0("g-and-k distribution n = ", n))

m_comp_df |>
  mutate(m = as.factor(m)) |>
  ggplot(aes(x = k, color = m)) +
  geom_density(linewidth = 1.1) +
  geom_vline(xintercept = true_k) +
  ggtitle(paste0("g-and-k distribution n = ", n))




```

```{r gandk_n100_comparison_tikz, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 3, fig.width = 5, dev = "tikz"}
par(mar = c(3.5, 3.8, 1.5, 1.1)) # bottom, left, top, right
par(mgp = c(2.15, 1, 0))
par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)



```


# n = 1000 {.tabset}

## Data generation

```{r data_sim_gandk_n1000, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}
set.seed(123)
n <- 1000
true_a <- 1.0
true_b <- 1.0
true_g <- 1.0
true_k <- 0.5

# Generate data using the R function
sim_data <- simulate_gandk_with_gradient(n, c(true_a, true_b, true_g, true_k))
y <- sim_data$samples
```

## PDMP 

### set-up 

```{r gandk_setup_n1000, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

# Sampler parameters
gamma <- median_heuristic(cbind(y,y))
m <- 5 # Number of synthetic samples
T_end <- 1000
w <- sqrt(2*pi)

# Helper function to transform from [0,5] to unconstrained
transform_to_unconstrained <- function(theta) {
  # θ = 5/(1+exp(-ξ)) => ξ = log(θ/(5-θ))
  log(theta / (5 - theta))
}

# Initial values on unconstrained scale
# Start near the middle of [0,5], e.g., at 2.5 for each parameter
xi_0 <- c(
  transform_to_unconstrained(1),  # a
  transform_to_unconstrained(1),  # b
  transform_to_unconstrained(1.0),  # g
  transform_to_unconstrained(1.0)   # k
)

theta_0 <- c(1, 1, 1, 1)  # Initial velocities

```

## m = 5 (Rcpp)

```{r gandk_skeleton_m5_n1000, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

m <- 5


timer_MMD_gandk_m5.start <- Sys.time()
skeleton_gandk_IntractLik_m5 <- ZigZag_MMD_RBF_gandk_cpp_arma(T_end, xi_0, theta_0, y, m, gamma, w = w, N_skeleton = 100000)
timer_MMD_gandk_m5.end <- Sys.time()

sample_gandk_IntractLik_m5 <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_gandk_IntractLik_m5$skeleton_T, skeleton_Xi = skeleton_gandk_IntractLik_m5$skeleton_Xi, skeleton_Theta = skeleton_gandk_IntractLik_m5$skeleton_Theta, N = 1000)


sample_gandk_IntractLik_m5_theta <- transform_samples_to_original_scale(sample_gandk_IntractLik_m5)


```

```{r gandk_m5_n1000_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}
difftime(timer_MMD_gandk_m5.end, timer_MMD_gandk_m5.start, units = "mins")

skeleton_gandk_IntractLik_m5$max_alpha
skeleton_gandk_IntractLik_m5$mean_alpha

plot(density(sample_gandk_IntractLik_m5_theta[,1]), ylab = "Density", xlab = paste0("a"), lwd = 3, main = paste("g-and-k"))
abline(v = true_a, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m5_theta[,2]), ylab = "Density", xlab = paste0("b"), lwd = 3, main = paste("g-and-k"))
abline(v = true_b, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m5_theta[,3]), ylab = "Density", xlab = paste0("g"), lwd = 3, main = paste("g-and-k"))
abline(v = true_g, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m5_theta[,4]), ylab = "Density", xlab = paste0("k"), lwd = 3, main = paste("g-and-k"))
abline(v = true_k, lwd = 3, lty = 2, col = "red")


ESS(sample_gandk_IntractLik_m5_theta[,1])
ESS(sample_gandk_IntractLik_m5_theta[,2])
ESS(sample_gandk_IntractLik_m5_theta[,3])
ESS(sample_gandk_IntractLik_m5_theta[,4])
```

## m = 20 (Rcpp)

```{r gandk_skeleton_m20_n1000, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

m <- 20


timer_MMD_gandk_m20.start <- Sys.time()
skeleton_gandk_IntractLik_m20 <- ZigZag_MMD_RBF_gandk_cpp_arma(T_end, xi_0, theta_0, y, m, gamma, w = w, N_skeleton = 100000)
timer_MMD_gandk_m20.end <- Sys.time()

sample_gandk_IntractLik_m20 <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_gandk_IntractLik_m20$skeleton_T, skeleton_Xi = skeleton_gandk_IntractLik_m20$skeleton_Xi, skeleton_Theta = skeleton_gandk_IntractLik_m20$skeleton_Theta, N = 1000)


sample_gandk_IntractLik_m20_theta <- transform_samples_to_original_scale(sample_gandk_IntractLik_m20)


```

```{r gandk_m20_n1000_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}
difftime(timer_MMD_gandk_m20.end, timer_MMD_gandk_m20.start, units = "mins")

skeleton_gandk_IntractLik_m20$max_alpha
skeleton_gandk_IntractLik_m20$mean_alpha

plot(density(sample_gandk_IntractLik_m20_theta[,1]), ylab = "Density", xlab = paste0("a"), lwd = 3, main = paste("g-and-k"))
abline(v = true_a, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m20_theta[,2]), ylab = "Density", xlab = paste0("b"), lwd = 3, main = paste("g-and-k"))
abline(v = true_b, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m20_theta[,3]), ylab = "Density", xlab = paste0("g"), lwd = 3, main = paste("g-and-k"))
abline(v = true_g, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m20_theta[,4]), ylab = "Density", xlab = paste0("k"), lwd = 3, main = paste("g-and-k"))
abline(v = true_k, lwd = 3, lty = 2, col = "red")


ESS(sample_gandk_IntractLik_m20_theta[,1])
ESS(sample_gandk_IntractLik_m20_theta[,2])
ESS(sample_gandk_IntractLik_m20_theta[,3])
ESS(sample_gandk_IntractLik_m20_theta[,4])
```

## m = 50  (Rcpp)

```{r gandk_skeleton_m50_n1000, include=TRUE, echo=TRUE, eval=TRUE, cache=TRUE}

m <- 50


timer_MMD_gandk_m50.start <- Sys.time()
skeleton_gandk_IntractLik_m50 <- ZigZag_MMD_RBF_gandk_cpp_arma(T_end, xi_0, theta_0, y, m, gamma, w = w, N_skeleton = 100000)
timer_MMD_gandk_m50.end <- Sys.time()

sample_gandk_IntractLik_m50 <- skeleton_to_sample_cpp_arma(skeleton_T = skeleton_gandk_IntractLik_m50$skeleton_T, skeleton_Xi = skeleton_gandk_IntractLik_m50$skeleton_Xi, skeleton_Theta = skeleton_gandk_IntractLik_m50$skeleton_Theta, N = 1000)


sample_gandk_IntractLik_m50_theta <- transform_samples_to_original_scale(sample_gandk_IntractLik_m50)


```

```{r gandk_m50_n1000_diag, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

difftime(timer_MMD_gandk_m50.end, timer_MMD_gandk_m50.start, units = "mins")

skeleton_gandk_IntractLik_m50$max_alpha
skeleton_gandk_IntractLik_m50$mean_alpha

plot(density(sample_gandk_IntractLik_m50_theta[,1]), ylab = "Density", xlab = paste0("a"), lwd = 3, main = paste("g-and-k"))
abline(v = true_a, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m50_theta[,2]), ylab = "Density", xlab = paste0("b"), lwd = 3, main = paste("g-and-k"))
abline(v = true_b, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m50_theta[,3]), ylab = "Density", xlab = paste0("g"), lwd = 3, main = paste("g-and-k"))
abline(v = true_g, lwd = 3, lty = 2, col = "red")

plot(density(sample_gandk_IntractLik_m50_theta[,4]), ylab = "Density", xlab = paste0("k"), lwd = 3, main = paste("g-and-k"))
abline(v = true_k, lwd = 3, lty = 2, col = "red")


ESS(sample_gandk_IntractLik_m50_theta[,1])
ESS(sample_gandk_IntractLik_m50_theta[,2])
ESS(sample_gandk_IntractLik_m50_theta[,3])
ESS(sample_gandk_IntractLik_m50_theta[,4])
```

COULD ADD N TO THESE DFS

```{r gandk_n1000_comparison, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE}

m5_df <- as.data.frame(sample_gandk_IntractLik_m5_theta) |> 
  mutate(m = rep(5, nrow(sample_gandk_IntractLik_m5_theta))) |>
  rename(a = V1, 
         b = V2, 
         g = V3, 
         k = V4)

m20_df <- as.data.frame(sample_gandk_IntractLik_m20_theta) |> 
  mutate(m = rep(20, nrow(sample_gandk_IntractLik_m20_theta))) |>
  rename(a = V1, 
         b = V2, 
         g = V3, 
         k = V4)

m50_df <- as.data.frame(sample_gandk_IntractLik_m50_theta) |> 
  mutate(m = rep(50, nrow(sample_gandk_IntractLik_m50_theta))) |>
  rename(a = V1, 
         b = V2, 
         g = V3, 
         k = V4)

m_comp_df <- bind_rows(m5_df, m20_df, m50_df)

m_comp_df |>
  mutate(m = as.factor(m)) |>
  ggplot(aes(x = a, color = m)) +
  geom_density(linewidth = 1.1) +
  geom_vline(xintercept = true_a) +
  ggtitle(paste0("g-and-k distribution n = ", n))

m_comp_df |>
  mutate(m = as.factor(m)) |>
  ggplot(aes(x = b, color = m)) +
  geom_density(linewidth = 1.1) +
  geom_vline(xintercept = true_b) +
  ggtitle(paste0("g-and-k distribution n = ", n))

m_comp_df |>
  mutate(m = as.factor(m)) |>
  ggplot(aes(x = g, color = m)) +
  geom_density(linewidth = 1.1) +
  geom_vline(xintercept = true_g) +
  ggtitle(paste0("g-and-k distribution n = ", n))

m_comp_df |>
  mutate(m = as.factor(m)) |>
  ggplot(aes(x = k, color = m)) +
  geom_density(linewidth = 1.1) +
  geom_vline(xintercept = true_k) +
  ggtitle(paste0("g-and-k distribution n = ", n))




```

```{r gandk_n1000_comparison_tikz, include=TRUE, echo=TRUE, eval=TRUE, cache=FALSE, fig.height = 3, fig.width = 5, dev = "tikz"}
par(mar = c(3.5, 3.8, 1.5, 1.1)) # bottom, left, top, right
par(mgp = c(2.15, 1, 0))
par(cex.lab = 1.25, cex.axis = 1.25, cex.main = 1.25)



```